%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Dr. Linda S. Rayor and Dr. Corrie Moreau} % Job title
    {Research Assistant} % Organization
    {Cornell University} % Location
    {February 2019 — Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Completed Senior Honor's Research Thesis studying the social and life-history evolution of huntsman spiders; manuscript in review.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Dr. Jason J. Dombroskie} % Job title
    {Research Assistant} % Organization
    {Cornell University Insect Collection} % Location
    {August 2016 — Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Described Neotropical species of \textit{Argyresthia} (Lepidoptera: Argyresthiidae) from Guatemala, in preparation for publication.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Dr. Nusha Keyghobadi} % Job title
    {Field Assistant} % Organization
    {Western University} % Location
    {June 2020 — July 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Assisted graduate student Shayla Kroeze and Dr. Nusha Keyghobadi with tissue sampling for population genetic study of the Mottled Duskywing, \textit{Erynnis martialis}, a species listed as Critically Imperiled in New York, since they could not cross the US-Canada border due to the COVID-19 pandemic.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Dr. Jason J. Dombroskie} % Job title
    {Curatorial Assistant} % Organization
    {Cornell University Insect Collection} % Location
    {August 2016 — June 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Undergraduate lead on an NSF-funded grant to curate the macrolepidoptera and database John G. Franclemon's slide collection of moth genitalia and corresponding specimens.}
        \item {Three families curated, totalling over 6,000 species, with curation protocol set in place ongoing for existing curation projects.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Dr. Bryan N. Danforth} % Job title
    {Lab Assistant} % Organization
    {Cornell University} % Location
    {August 2018 — March 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked to identify thousands of bees collected by New York State Department of Environmental Conservation for the Empire State Native Pollinator Survey, a project of the New York Natural Heritage Program.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Dr. Lauren Esposito} % Job title
    {NSF Research Experiences for Undergraduates Intern} % Organization
    {California Academy of Sciences} % Location
    {June 2019 — August 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Investigated the niche ecology of scorpions in the Bay Area and used genetic techniques (Sanger sequencing, etc.) to examine population genetics.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Dr. Laura Harrington} % Job title
    {Curatorial Assistant} % Organization
    {Cornell University} % Location
    {January 2019 - May 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Curated and inventoried Cornell University Medical and Veterinary Entomology Collection, containing over 9,600 specimens and 665 species, including medically important arthropods, diseases, and conditions.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Dr. Lauren Esposito} % Job title
    {Field Assistant} % Organization
    {California Academy of Sciences} % Location
    {July 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Collected nearly 150 scorpions in the genus \textit{Centruoides} nightly for a two-week period at the UNAM Field Station in Los Tuxtlas, Veracruz, Mexico with graduate student Aaron Goodman.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Dr. Linda S. Rayor} % Job title
    {Lab Assistant \& Museum Preparator} % Organization
    {Cornell University} % Location
    {June 2017 — January 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Trained in arthropod husbandry practices, including maintenance of live arachnids and insects. Collaborated with a team that collected and prepared over 350 dried spider specimens prepared in a lifelike position for The Australian Museum’s \textit{Spiders: Fear and Fascination} traveling museum exhibit.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Anne W. Mitchell \& Louise Stoney} % Job title
    {Website Manager} % Organization
    {Alliance for Early Childhood Finance} % Location
    {2015 — 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Updated and maintained website by fixing broken links, uploading missing files, updating newsletter mailings, and proofreading the site.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Robert Henry} % Job title
    {Production Technician} % Organization
    {GlaxoSmithKline, PLC} % Location
    {July 2016 — August 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked in a FDA-regulated facility at GSK's Consumer Healthcare Manufacturing plant in Oak Hill, NY as a production technician in the packaging department for Aquafresh®  and Sensodyne® toothpaste products.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
