%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Outreach \& Media}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {KQED} % Job title
    {\emph{Scorpions are Predators with a Sensitive Side} YouTube Video} % Organization
    {San Francisco, CA} % Location
    {March 2021 — October 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Consulted with Dr. Lauren Esposito for KQED \href{https://www.youtube.com/watch?v=3jtm9BdnE1U}{\underline{video}} about scorpion sensory systems.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Department of Entomology} % Job title
    {Insectapalooza} % Organization
    {Cornell University} % Location
    {2016 — 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Engaged with thousands of attendees at annual Insectapalooza event about the Cornell University Insect Collection and live arachnids from the Rayor Lab.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Kate Lindsay \& Stephen A. Marshall} % Job title
    {\emph{Laphria} Photo Featured in Paper} % Organization
    {Canadian Journal of Arthropod ID} % Location
    {2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Photo of \emph{Laphria champlainii} featured in \href{https://cjai.biologicalsurvey.ca/lm_37/lm_37.pdf}{\underline{paper}}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Dr. Linda S. Rayor} % Job title
    {Naturalist Outreach Practicum} % Organization
    {Cornell University} % Location
    {August 2018 — December 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Student in Dr. Linda S. Rayor's Naturalist Outreach Practicum. Developed skills in delivering effective outreach to a variety of ages and outreach engagements. Created programs focused on general entomology and fossils of New York State. Gave a total of fifteen talks, eight of which were geared toward elementary-aged students in central New York.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Kate Klein for the Cornell Chronicle} % Job title
    {\emph{Homecoming 2018: community and fun enhanced by history} Article} % Organization
    {Cornell University} % Location
    {27 September 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Photographed in \href{https://news.cornell.edu/stories/2018/09/homecoming-2018-community-and-fun-enhanced-history}{\underline{piece}} doing outreach with the undergraduate entomology club, Snodgrass and Wigglesworth.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Hugh W. Gregg Elementary School} % Job title
    {Insects and Entomology Presentation} % Organization
    {Corning, NY} % Location
    {2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Spoke to fifth grade classes about insects and the field of entomology with Casey Hale.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Johnny Chen} % Job title
    {\emph{Entomology At Cornell} YouTube Video} % Organization
    {Cornell University Insect Collection} % Location
    {9 March 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Featured in and helped create a \href{https://www.youtube.com/watch?v=SAqNvSO6Ulg}{\underline{video}} about the insect collection at Cornell University.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Blaine Friedlander for the Cornell Chronicle} % Job title
    {\emph{It’s alive: Students snare spiders for museum exhibit} Article} % Organization
    {Cornell University} % Location
    {19 February 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Quoted and photographed in a \href{https://news.cornell.edu/stories/2018/02/its-alive-students-snare-spiders-museum-exhibit}{\underline{piece}} about preparing the \emph{Spiders: Fear and Fascination} traveling museum exhibit.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Teá Kesting-Handly} % Job title
    {Sphingidae Image Contribution} % Organization
    {Sphingidae.us} % Location
    {2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided images of adult and larval Sphingidae for \href{sphingidae.us}{\underline{website}} focusing on diversity, ecology, and identification of Sphingidae in the United States.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Locally Sourced Science} % Job title
    {\emph{Gina goes to “Moth night”}} % Organization
    {WFRI Community Radio} % Location
    {Summer 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Featured in WFRI Community Radio’s Locally Sourced Science \href{https://www.mixcloud.com/Locally_Sourced_Science/ep-16-lss-tours-cornells-lake-source-cooling-plant-with-lanny-joyce-gina-goes-to-moth-night/}{\underline{coverage}} of a moth night.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {John Burroughs Natural History Society} % Job title
    {Welcome to the Dark Side: An Adventure Inside the World of Moths} % Organization
    {Kingston, NY} % Location
    {19 September 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Spoke to members about moth ecology.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Huyck Preserve and Biological Research Station} % Job title
    {Wildlife Ecology: Welcome to the Dark Side: An Adventure Inside the World of Moths} % Organization
    {Rensselaerville, NY} % Location
    {Summer 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Spoke to two cohorts of high school students in summer program about moth ecology. 17 July 2015 and 14 August 2015.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Audrey Matott for the Daily Mail} % Job title
    {\emph{The Mothman proposal: Insect good for the environment} Article} % Organization
    {Catskill, NY} % Location
    {7 July 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Profiled in local newspaper about work with National Moth Week.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {High Technology High School} % Job title
    {National Moth Week Presentation} % Organization
    {Lincroft, NY (via Skype)} % Location
    {23 October 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Spoke to dozens of students about citizen science and National Moth Week.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Scott M. Ellis Elementary} % Job title
    {Insects and Entomology Presentation} % Organization
    {Greenville, NY} % Location
    {13 September 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Spoke to second grade elementary class about insects and the field of entomology.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
