%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Service}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {National Moth Week} % Job title
    {Team Member} % Organization
    {} % Location
    {2015 — Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead initiatives with partner community science organizations to encourage people to submit observations to platforms such as iNaturalist and Project Noah.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Snodgrass and Wigglesworth Undergraduate Entomology Club} % Job title
    {President} % Organization
    {Cornell University} % Location
    {January 2018 — December 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Co-planned outreach and club events as well as the annual spring break trip which entailed visiting other entomology departments. Led effort to move up a student organization funding tier.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Student Library Advisory Committee} % Job title
    {Trustee} % Organization
    {Cornell University} % Location
    {August 2017 — May 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Voiced student concerns to administration about issues and items related to the library.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {College of Agriculture and Life Sciences} % Job title
    {CALS Ambassador} % Organization
    {Cornell University} % Location
    {2017 — 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Communicated resources and opportunities at the College of Agriculture and Life Sciences to prospective students and their families.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Greenville Educational Foundation} % Job title
    {Trustee} % Organization
    {Greenville Central School District} % Location
    {2014 — 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Served as a student representative to direct resources for enhancing the educational experience of students throughout the district.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Mothapalooza} % Job title
    {Event Guide} % Organization
    {Ohio} % Location
    {2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Co-led a tour for annual Mothapalooza event and helped share moth identification tips. Presented about community science and National Moth Week.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
