%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Talks}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------\
\bodyfontlight\tiny\item\ Asterisk (\text{*}) indicates presenter.

\color{darktext}\small\textbf{Oral Papers}
\begin{enumerate}
\bodyfontlight\scriptsize\item\textbf{Gorneau, J.A.*}, Rayor, L.S., Moreau, C.S. The evolution of huntsman spiders (Araneae: Sparassidae): insights into life history. American Arachnological Society Virtual Summer Symposium. 2020.
\bodyfontlight\scriptsize\item\textbf{Gorneau, J.A.*}, Rayor, L.S., Moreau, C.S. The evolution of huntsman spiders (Araneae: Sparassidae): insights into life history. Cornell Entomology Undergraduate Honors Thesis Symposium. 2020.
\bodyfontlight\scriptsize\item\textbf{Gorneau, J.A.*}, Tartaglia, E. National Moth Week: Leveraging Citizen Science Data to Understand Bias and Biodiversity. Ninth Annual Cornell Entomology Symposium at Cornell University in Ithaca, New York, USA. 2020.
\bodyfontlight\scriptsize\item\textbf{Gorneau, J.A.}, Goodman, A.M.*, Esposito, L.A. Niche partitioning among three vaejovid scorpions near the San Francisco Bay Area (Scorpiones: Vaejovidae). Mary Bowerman Research Symposium, California, USA. 2019.
\bodyfontlight\scriptsize\item\textbf{}Rayor, L.S.*, \textbf{Gorneau, J.A.}, Moreau, C.S. Trait-mapping sociality and life-history adaptations in social and solitary huntsman spiders. Animal Behavior Society in Chicago, Illinois, USA. 2019.
\end{enumerate}
\small\textbf{Posters}
\begin{enumerate}
\bodyfontlight\scriptsize\item\textbf{Gorneau, J.A.*}, Goodman, A.M., Esposito, L.A. Niche partitioning among three vaejovid scorpions near the San Francisco Bay Area (Scorpiones: Vaejovidae). SACNAS National Diversity in STEM Conference in Honolulu, Hawaii, USA. 2019.
\bodyfontlight\scriptsize\item\textbf{Gorneau, J.A.*}, Goodman, A.M., Esposito, L.A. Niche partitioning among three vaejovid scorpions near the San Francisco Bay Area (Scorpiones: Vaejovidae). Cornell Undergraduate Research Board (CURB) Fall Forum at Cornell University in Ithaca, New York, USA. 2019.
\end{enumerate}
