%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Teaching}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {ENTOM 2100 (Dr. Marina Caillaud \& Dr. Laura Harrington)} % Job title
    {Plagues and People Teaching Assistant} % Organization
    {Cornell University} % Location
    {August 2019 — December 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Co-led weekly discussion section and participated in active learning lecture environment in non-major class focusing on disease pathology, transmission, and human impacts.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {ENTOM 2150/3150 (Dr. Linda S. Rayor)} % Job title
    {Spider Biology Teaching Assistant} % Organization
    {Cornell University} % Location
    {August 2018 — December 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Prepared displays for class, educated students on dichotomous keys and spider identiifcation, co-led field trips, and heled with open lab activities for class including both majors and non-majors.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {ENTOM 2010/2011 (Dr. Marina Caillaud \& Dr. Bryan N. Danforth)} % Job title
    {Alien Empire Teaching Assistant} % Organization
    {Western University} % Location
    {January 2018 — May 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Co-led weekly discussion section, took attendance, graded worksheets and exams in non-major class providing a broad overview of insects.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {ENTOM 2120 (Dr. Cole Gilbert)} % Job title
    {Insect Biology Teaching Assistant} % Organization
    {Cornell Univeristy Insect Collection} % Location
    {August 2017 — December 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Helped prepare labs, taught students how to use a dichotomous key, and helped prepare lab practical stations for majors class.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
\end{cventries}
